Untitled

### 2022-12-17 Figuring_Q3.Rmd
Starting to work on code producing pdf report

###Testing 
#Initial values
#finding prob of sequence under current pt
X <- read.table("q3Weather.txt",header = F)
X <- X$V1
initPT <- matrix(1/3,nrow=3,ncol=3)
initStateProbs <- c(1/3,1/3,1/3)
n <- 100
burnin <- 5

@@

proposal <- matrix(NA,ncol=3,nrow=3)
#starting loop
j=2
    #Generating proposal value for each row of transition matrix
    for (i in 1:length(initStateProbs)){
      proposal[i,] <- simDirichletRV(20*V[i,,j-1])
    }
     #calculating alpha

      #Generating posterior using equation (12) for proposal and old value of PT
      actualp.prev <- actualp.prop <- NULL
      for (i in 1:length(init.state)){
        actualp.prev[i] <- V[init.state[i],trans.state[i],j-1]
        actualp.prop[i] <- proposal[init.state[i],trans.state[i]]
      }
      #density has some constant as proportional but due to fraction constant cancels out so dont
      #need to worry about it
      true.density.prev <- prod(actualp.prev)*initStateProbs[X[1]]
      true.density.prop <-prod(actualp.prop)*initStateProbs[X[1]]
      true.density.prop/true.density.prev

      #Doing shady stuff (assuming that px` or previous is the x vector :P)
      calcDirichletPDF(x=proposal[2,],a=V[2,,j-1])

# A <- array(NA,dim=c(3,3,n+burnin+1))
# A[,,1] <- matrix(c(1,2,3,4,5,6,7,8,9),ncol=3,nrow=3,byrow = T)
# #1st index is row
# A[1,,1]
# #2nd index is column
# A[,1,1]
```

>>>>

###Testing 
#Initial values
#finding prob of sequence under current pt
X <- read.table("q3Weather.txt",header = F)
X <- X$V1
initPT <- matrix(1/3,nrow=3,ncol=3)
initStateProbs <- c(1/3,1/3,1/3)
n <- 500000
burnin <- 5

@@

  #initializing algorithm
  V <- array(NA,dim=c(3,3,n+burnin+1))
  V[,,1] <- initStateProbs
  est.state.prob <- array(NA,dim=c(1,3,n+burnin+1)) 
  est.state.prob[,,1] <-  initStateProbs

proposal <- matrix(NA,ncol=3,nrow=3)
#starting loop
for (j in 2:(n+burnin+1)){

    est.state.prob[,,j] <- est.state.prob[,,j-1]%*%V[,,j-1]
    #Generating proposal value for each row of transition matrix
    for (i in 1:length(initStateProbs)){
      proposal[i,] <- simDirichletRV(20*V[i,,j-1])
    }
     #calculating alpha

      #Generating posterior using equation (12) for proposal and old value of PT
      actualp.prev <- actualp.prop <- NULL
      for (i in 1:length(init.state)){
        actualp.prev[i] <- V[init.state[i],trans.state[i],j-1]
        actualp.prop[i] <- proposal[init.state[i],trans.state[i]]
      }
      #density has some constant as proportional but due to fraction constant cancels out so dont
      #need to worry about it
      true.density.prev <- prod(actualp.prev)*initStateProbs[X[1]]
      true.density.prop <-prod(actualp.prop)*initStateProbs[X[1]]
      #alpha <- true.density.prop/true.density.prev

      #Doing shady stuff (assuming that px` or previous is the x vector :P)
      #Calculating pdf under proposal using x as the probability to be in each state 
       prop.density.prop <- exp(calcDirichletPDF(x=proposal[2,],a=est.state.prob[,,j-1])+
                                  calcDirichletPDF(x=proposal[1,],a=est.state.prob[,,j-1])+calcDirichletPDF(x=proposal[3,],a=est.state.prob[,,j-1]))
      # #same but under previous accepted value
       prop.density.prev <- exp(calcDirichletPDF(x=V[2,,j-1],a=est.state.prob[,,j-1])+
                                 calcDirichletPDF(x=V[1,,j-1],a=est.state.prob[,,j-1])+calcDirichletPDF(x=V[3,,j-1],a=est.state.prob[,,j-1]))

      # alpha <- (true.density.prop*prop.density.prev)/(true.density.prev*prop.density.prop)
      alpha <-  prop.density.prop/prop.density.prev

      if(min(1,alpha)>=runif(1)){
        V[,,j] <- proposal
      }else{
        V[,,j] <- V[,,j-1]
      }
}

# A <- array(NA,dim=c(3,3,n+burnin+1))
# A[,,1] <- matrix(c(1,2,3,4,5,6,7,8,9),ncol=3,nrow=3,byrow = T)
# #1st index is row
# A[1,,1]
# #2nd index is column
# A[,1,1]

plot(V[1,2,],type="l") #No convegerence :(
```
